Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-06-01 Methods-and-Results.Rmd
tbl lab

The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment. For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis. As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency. The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations. Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020. The full preregistration is available at \citet[][]{KreienkampMasked2021f}. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

```{r descrFullWide, include=FALSE}
# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
rbind(
  workerMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentMlCor %>%
    select(names(workerMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalMlCor %>%
    select(names(workerMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  allMlCor %>%
    select(names(workerMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean")
) %>%
  kbl(.,
      format = "latex",
      caption = "Full Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
  pack_rows("Study 2", ncol(workerMlCor) + 1,
            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>%
  pack_rows("Across Studies", sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor)) + 1,  
            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor), ncol(allMlCor))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrFullWide.tex")
```

@@

# Outgroup Interaction Sample Descriptives Table --- wider version
rbind(
  workerOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentOutMlCor %>%
    select(names(workerOutMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  allOutMlCor %>%
    select(names(workerOutMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean")
) %>%
  kbl(.,
      format = "latex",
      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
  pack_rows("Across Studies", sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor), ncol(allOutMlCor))) %>% 
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWide.tex")

>>>>

The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an intensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment. For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis. As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency. The intensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations. Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020. The full preregistration is available at \citet[][]{KreienkampMasked2021f}. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

```{r descrFullWide, include=FALSE}
# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
rbind(
  workerMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentMlCor %>%
    select(names(workerMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalMlCor %>%
    select(names(workerMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  allMlCor %>%
    select(names(workerMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean")
) %>%
  kbl(.,
      format = "latex",
      caption = "Full Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
  pack_rows("Study 2", ncol(workerMlCor) + 1,
            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>%
  pack_rows("Across Studies", sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor)) + 1,  
            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor), ncol(allMlCor))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Within-person correlations;",
      "Lower triangle: Between-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrFullWide.tex")
```

@@

# Outgroup Interaction Sample Descriptives Table --- wider version
rbind(
  workerOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentOutMlCor %>%
    select(names(workerOutMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  allOutMlCor %>%
    select(names(workerOutMlCor)) %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean")
) %>%
  kbl(.,
      format = "latex",
      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
  pack_rows("Across Studies", sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor), ncol(allOutMlCor))) %>% 
  footnote(
    general = c(
      "Upper triangle: Within-person correlations;",
      "Lower triangle: Between-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWide.tex")

### 2023-06-01 Robustness-Methods-and-Results.Rmd
Update Robustness-Methods-and-Results.Rmd
tbl lab

>>>>

```{r}
#| label: descrFullWideAppB
#| include: false

vars_full <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Outgroup Interaction" = "OutgroupInteraction",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 1),
    id = "PID",
    selection = setdiff(as.character(vars_full), c("InteractionAccidental", "Quality")),
    labels = setdiff(names(vars_full), c("Accidental", "Quality"))
  ) 
s2_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 2),
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  ) 
s3_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 3),
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  ) 
all_MlCor_full <- 
  MlCorMat(
    data = dt_exp_all,
    id = "PID",
    selection = as.character(vars_full),
    labels = names(vars_full)
  )

rbind(
  s1_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Accidental = "",
               .before = "Attitudes NL") %>%
    add_column(Quality = "",
               .before = "Attitudes NL"),
  s2_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s3_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  all_MlCor_full %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Full Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(s3_MlCor_full),
      "Descriptives" = nrow(s3_MlCor_full) - ncol(s3_MlCor_full)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(s1_MlCor_full)) %>%
  pack_rows("Study 2", ncol(s1_MlCor_full) + 1,
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full))) %>%
  pack_rows("Study 3", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full)) + 1,  
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full))) %>%
  pack_rows("Across Studies", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full)) + 1,  
            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full), ncol(all_MlCor_full))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Within-person correlations;",
      "Lower triangle: Between-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05",
      "Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrFullWideAppB.tex")

```{r}
#| label: descrOutWideAppB
#| include: false

vars_out <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Practical Need" = "practical_need_dum",
  "Psychological Need" = "psychological_need_dum",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s2_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s3_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
all_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  )

rbind(
  s1_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s2_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  s3_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable"),
  all_MlCor_out %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      caption = "Outgroup Interaction Sample: Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(s3_MlCor_out),
      "Descriptives" = nrow(s3_MlCor_out) - ncol(s3_MlCor_out)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(s1_MlCor_out)) %>%
  pack_rows("Study 2", ncol(s1_MlCor_out) + 1,
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out))) %>%
  pack_rows("Study 3", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out)) + 1,  
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out))) %>%
  pack_rows("Across Studies", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out)) + 1,  
            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out), ncol(all_MlCor_out))) %>% # fix table position
  footnote(
    general = c(
      "Upper triangle: Within-person correlations;",
      "Lower triangle: Between-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutWideAppB.tex")
